We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-31 paper/paper.tex
edit

Figure \ref{fig:correlations_illustrisdm} illustrates the results from
 compute the covariance matrix and mean vector in
 Eq.\ref{eq:multivariate} from the normalized quantities in the
 simulation.   
The distributions are computed from $10^6$ with the multivariate
gaussian.

>>>>

Figure \ref{fig:correlations_illustrisdm} illustrates the results from
 compute the covariance matrix and mean vector in
 Eq.\ref{eq:multivariate} from the normalized quantities computed from
 the Illlustris1-Dark simulation.
The distributions in the Figure are computed from $10^6$ with the multivariate
gaussian. 
Similar plots for Illustris1 and ELVIS are in the Appendix.
The values for all the covariance matrices and mean vectors for all
the simulations are listed in the Appendix.

This results nicely summarizes the results we had in the previous
sections. 
The left triangular plot shows how M31 falls into the middle of all 2D
distributions always close to the peak and within the $1-\sigma$
range. 
The right plot clearly places the MW observations outside the
$3\sigma$ range in the joint distributions that involve the width
$w$.

In both cases the strongest positive correlation is present for the
